---
title: "os-health"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{os-health}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(dplyr)
library(GithubMetrics)
```

## Intro

The following vignette shows how the OS Health is calculated, with the aim of 
capturing the current vibrancy of the packages community, and their activity on 
the repo. 

It is important to note that 'OS Health' is not equivalent to metrics 
assessed in `riskmetric`. An example being a stable and mature statistical R 
package that could be orphaned, or stable enough activity has largely ended. 
In terms of 'OS Health', the developer community is not active - but 
the package itself could still be robust and meeting all it's intended use 
cases (OS Health and the scope of `riskmetric` would overlap though if 
the package has stale open issues that are being ignored).

> Note - in the 
context of openpharma.github.io and the pharmaverse.org, we may deprecate using 
this package and move to GrimoreLab tooling.

## Get data

```{r, eval = FALSE}
# repos
  repos <- c(
    "Roche/crmPack" ,
    "Roche/rtables",
    "openpharma/visR",
    "openpharma/GithubMetrics",
    "pharmaverse/admiral"
  )

# commits
  commits <- gh_commits_get(
    repos,
    days_back = 365*10
  )

# issues
  issues <- gh_issues_get(repos, days_back =  365*10)
```

## Create metrics

```{r}
issues_enriched <- issues %>%
  mutate(
    days_open = as.numeric(Sys.Date() - as.Date(created)),
    days_no_activity = as.numeric(Sys.Date() - as.Date(updated))
  ) %>%
  select(
    full_name, state, days_open, days_no_activity
  )

commits_enriched <- commits %>%
  mutate(
    date = as.Date(datetime)
  ) %>%
  select(full_name, date, author)

scoring <- tibble(
  full_name = unique(commits$full_name)
  ) %>%
  left_join(
    gh_metric_issues(issues_enriched), by = "full_name"
  ) %>%
  left_join(
    gh_metric_commits_days_since_commit(commits_enriched), by = "full_name"
  ) %>%
  left_join(
    gh_metric_commits_prepost_midpoint(commits_enriched), by = "full_name"
  ) %>%
  left_join(
    gh_metric_commits_authors_ever(commits_enriched), by = "full_name"
  ) %>%
  left_join(
    gh_metric_commits_authors_prepost_midpoint(commits_enriched), by = "full_name"
  ) %>%
  gh_score()
```

## Results

These results were generated at `r Sys.time()`.

```{r}
scoring %>% select(full_name, score) %>%
  knitr::kable(
    caption = "OS Health Score"
  )
```

### Negative factors lowering OS health.

```{r, results='asis'}
for (i in 1:nrow(scoring)){
  cat(glue::glue("

*{scoring[i,]$full_name}*
    
* Score is {scoring[i,]$score}  
{scoring[i,]$warnings}
    
    
  "))
}
```


